State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added table for estimates in resutls
editted table with estimates
for merge with Parham

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of 2.5~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviations 2.88, 1.99 and 0.08\parham{(0.0829)} respectively.  \dean{ for discussion: indicating good results}. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

>>>>

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The mean parameter estimates and the corresponding standard deviations are given in Table~\ref{tab:Parameters estimates}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are close to the actual values, however show a small bias (with a mean bias of 2.5~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian. The mean parameter estimates are in good accordance with the actual values, with biases of 2.778, 7.138,  \dean{ for discussion: indicating good results}. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

\begin{table}
\centering
\begin{tabular}{cccc}
	\hline\hline Parameter & Actual Value & Mean Estimate & Standard Deviation \\
	\hline\hline
 	$\xi$ & 0.9 & 0.925 & 0.004 \\
	$\theta_0$ & 10 & 10.295 & 2.879 \\
	$\theta_1$ & -8 & -8.571 & 1.996 \\
	$\theta_2$ & 0.5 & 0.551 & 0.083 \\
\end{tabular}
\caption{Actual parameter values and mean parameter estimates and standard deviation.}
\label{tab:Parameters estimates}
\end{table}
